Equivalence Testing and the Second Generation \emph{P}-Value

### 2019-04-11 manuscript.Rmd
.
Correcting "50% of the correlation will fall" into "36% of the correlation will fall..."

As can be seen in Figure \ref{fig:TOSTSGPV12}, the two second generation *p*-values associated with the observed correlations at r = -0.45 and r = 0.45 are larger than 50%. Because the confidence intervals are asymmetric around the observed effect size of 0.45 (ranging from `r round(res$LL_CI_TTEST,2)` to `r round(res$UL_CI_TTEST,2)`) according to @blume_second-generation_2018 `r round(sgpv*100,3)`% of the data-supported hypotheses are null hypotheses, and therefore `r round(sgpv,3)*100`% of the data-supported hypotheses are compatible with the null premise. The further away from 0, the larger the SGPV when the observed mean falls on the equivalence bound. The SGPV is the proportion of values in a 95% confidence interval that overlap with the equivalence range, but not the probability that these values will be observed. In the most extreme case (i.e., a sample size of 4, and equivalence bounds set to r = -0.99 and 0.99, with an observed correlation of 0.99) `r round(sgpv2,3)*100`% of the confidence interval overlaps with the equivalence range, even though in the long run only 50% [UNTRUE: this is about 36% of the observed correlations... once again, due to asymmetric CI around r] of the correlations observed in the future will fall in this range.

>>>>

As can be seen in Figure \ref{fig:TOSTSGPV12}, the two second generation *p*-values associated with the observed correlations at r = -0.45 and r = 0.45 are larger than 50%. Because the confidence intervals are asymmetric around the observed effect size of 0.45 (ranging from `r round(res$LL_CI_TTEST,2)` to `r round(res$UL_CI_TTEST,2)`) according to @blume_second-generation_2018 `r round(sgpv*100,3)`% of the data-supported hypotheses are null hypotheses, and therefore `r round(sgpv,3)*100`% of the data-supported hypotheses are compatible with the null premise. The further away from 0, the larger the SGPV when the observed mean falls on the equivalence bound. The SGPV is the proportion of values in a 95% confidence interval that overlap with the equivalence range, but not the probability that these values will be observed. In the most extreme case (i.e., a sample size of 4, and equivalence bounds set to r = -0.99 and 0.99, with an observed correlation of 0.99) `r round(sgpv2,3)*100`% of the confidence interval overlaps with the equivalence range, even though in the long run approximately 36% of the correlations observed in the future will fall in this range.

### 2019-04-11 manuscript.tex
Correcting "50% of the correlation will fall" into "36% of the correlation will fall..."

As can be seen in Figure \ref{fig:TOSTSGPV12}, the two second generation \emph{p}-values associated with the observed correlations at r = -0.45 and r = 0.45 are larger than 50\%. Because the confidence intervals are asymmetric around the observed effect size of 0.45 (ranging from 0.60 to 1) according to Blume et al. (2018) 58.11\% of the data-supported hypotheses are null hypotheses, and therefore 58.10\% of the data-supported hypotheses are compatible with the null premise. The further away from 0, the larger the SGPV when the observed mean falls on the equivalence bound. The SGPV is the proportion of values in a 95\% confidence interval that overlap with the equivalence range, but not the probability that these values will be observed. In the most extreme case (i.e., a sample size of 4, and equivalence bounds set to r = -0.99 and 0.99, with an observed correlation of 0.99) 97.60\% of the confidence interval overlaps with the equivalence range, even though in the long run only 50\% of the correlations observed in the future will fall in this range.

>>>>

As can be seen in Figure \ref{fig:TOSTSGPV12}, the two second generation \emph{p}-values associated with the observed correlations at r = -0.45 and r = 0.45 are larger than 50\%. Because the confidence intervals are asymmetric around the observed effect size of 0.45 (ranging from 0.60 to 1) according to Blume et al. (2018) 58.11\% of the data-supported hypotheses are null hypotheses, and therefore 58.10\% of the data-supported hypotheses are compatible with the null premise. The further away from 0, the larger the SGPV when the observed mean falls on the equivalence bound. The SGPV is the proportion of values in a 95\% confidence interval that overlap with the equivalence range, but not the probability that these values will be observed. In the most extreme case (i.e., a sample size of 4, and equivalence bounds set to r = -0.99 and 0.99, with an observed correlation of 0.99) 97.60\% of the confidence interval overlaps with the equivalence range, even though in the long run only 50\% {[}UNTRUE: this is about 36\% of the observed correlations\ldots{} once again, due to asymmetric CI around r{]} of the correlations observed in the future will fall in this range.
